Analysis

### 2022-07-05 manuscript/manuscript_bioinformatics.Rmd
Minor tweaks

Our goal was to provide easy programmatic access to CTCF binding data applicable to any cell or tissue type. The CTCF package contains 43 GRanges objects of strand-specific CTCF motifs predicted using 98 PWMs from six databases on human and mouse genome assemblies, including the T2T and mm39 assemblies (`Table S3`). Given the popularity of the JASPAR database, we recommend using predictions made with the MA0139.1 PWM, selecting sites detected at 1E-6 p-value cutoff, and merging overlapping sites. If experimentally detected CTCF sites are of interest, we suggest using CTCF-bound cCREs from the ENCODE SCREEN database. We hope the CTCF package will enable standardization and reproducibility of studies employing CTCF binding data.

>>>>

Our goal was to provide easy programmatic access to CTCF binding data applicable to any cell or tissue type. The CTCF package contains 51 GRanges objects of strand-specific CTCF motifs predicted using 98 PWMs from six databases on human and mouse genome assemblies, including the T2T and mm39 assemblies (`Table S3`). Given the popularity of the JASPAR database, we recommend using predictions made with the MA0139.1 PWM, selecting sites detected at 1E-6 p-value cutoff, and merging overlapping sites. If experimentally detected CTCF sites are of interest, we suggest using CTCF-bound cCREs from the ENCODE SCREEN database. We hope the CTCF package will enable standardization and reproducibility of studies employing CTCF binding data.
